\section{Unitary Representations of the Poincaré Group}
Moving to the quantum theory, as already discussed, \emph{Wigner's theorem} states that continuous symmetries must be implemented by unitary operators on the state space. Since Poincaré group is non-compact, due to the presence of the boosts, all unitary representations must be infinite dimensional. In quantum field theory, fields are promoted to operators which act on the Fock space. The classical action which describes the system is constructed to be Poincaré invariant, therefore, by Noether's theorem, there will be conserved charges, which will be functions of the fields. Those, after quantisation, become hermitian operators on the Fock space and furnish a unitary representation of the Poincaré algebra on the state space. In particular, calling $\hat{M}^{\mu\nu}$ the generators of Lorentz transformations and $\hat{P}^\mu$ those of the translations, we'll have, for an infinitesimal transformation (cfr.~\eqref{eq:infinitesimal-poicare-transformation})
\begin{equation}
    U(\Lambda,a) = e^{\frac{i}{2} \omega_{\mu\nu} \hat{M}^{\mu\nu} + i \epsilon_\mu \hat{P}^\mu} \simeq 1 + \frac{i}{2} \omega_{\mu\nu} \hat{M}^{\mu\nu} + i \epsilon_\mu \hat{P}^\mu .
\end{equation}

To find out the irreducible state space, we want to work with operators which commute with each other, so that states in different such states won't transform into each other. Since $\comm{\hat{P}^\mu}{\hat{P}^\nu} = 0$, it's natural to express physical state vectors in terms of eigenvectors of $\hat{P}^\mu$. We'll further denote with $\sigma$ all the other quantum numbers necessary to describe the state. We're interested in \emph{one-particle states}, which in QFT are defined, in a free theory, as eigenstates of the number operator of eigenvalue one. For such a state, the labels $\sigma$ must be \emph{discrete}. Therefore, we start from
\begin{equation}\label{eq:unitary-poincare-eigenstate-momentum}
    \hat{P}^\mu \ket{p,\sigma} = p^\mu \ket{p,\sigma} .
\end{equation}

Pure translations form an abelian subgroup of the Poincaré group and are represented, on the state space, by
\begin{equation}\label{eq:unitary-poincare-translations}
    U(1, a) = e^{-i \epsilon_\mu \hat{P}^\mu} .
\end{equation}
Combining~\eqref{eq:unitary-poincare-eigenstate-momentum} with~\eqref{eq:unitary-poincare-translations}, we can explicitly see how a state transforms under translations
\begin{equation}\label{eq:unitary-poincare-state-translation}
    U(1,a)\ket{p,\sigma} = e^{-i \epsilon_\mu \hat{P}^\mu} \ket{p,\sigma} = e^{-i \epsilon_\mu p^\mu} \ket{p,\sigma} .
\end{equation}

We must, then find, how such states transform under a Lorentz transformation. We can easily see that acting on $\ket{p,\sigma}$ with a pure Lorentz transformation $U(\Lambda,0) \coloneq U(\Lambda)$, produces an eigenstate of $\hat{P}^\mu$ of eigenvalue $\Lambda p$:
\begin{equation}
    \hat{P}^\mu U(\Lambda) \ket{p,\sigma} = \tensor{\Lambda}{^\mu_\rho} p^\rho U(\Lambda) \ket{p,\sigma}
\end{equation}
\begin{proof}
    \begin{equation*}
    \begin{split}
        \hat{P}^\mu U(\Lambda) \ket{p,\sigma} &= U(\Lambda) \left[U^{-1} \hat{P}^\mu U(\Lambda)\right] \ket{p,\sigma} = U(\Lambda) \left[ \tensor{(\Lambda^{-1})}{_\rho^\mu} \hat{P}^\rho \right] \ket{p,\sigma}  \\
        &= \tensor{\Lambda}{^\mu_\rho} p^\rho U(\Lambda) \ket{p,\sigma} .
    \end{split}
    \end{equation*}
    where we used $U^{-1}U=\1$ in the first equality, eq.\color{red}\dots\dots\color{black} in the second, and finally eq.~\eqref{eq:unitary-poincare-eigenstate-momentum}, together with the well-known relation $\tensor{(\Lambda^{-1})}{_\rho^\mu} = \tensor{\Lambda}{^\mu_\nu}$
\end{proof}

Hence, because of eq.~\eqref{eq:unitary-poincare-eigenstate-momentum}, $U(\Lambda)\ket{p,\sigma}$ must be a linear combination of $\ket{\Lambda p,\sigma}$:
\begin{equation}\label{eq:temp-1}
    U(\Lambda)\ket{p,\sigma} =  \sum_{\sigma'} C_{\sigma' \sigma} (\Lambda, p) \ket{\Lambda p,\sigma'}.
\end{equation}

In general, by using suitable linear combinations of the $\ket{p,\sigma}$, it may be possible to choose the $\sigma$ labels in such a way that the matrix $C_{\sigma' \sigma} (\Lambda, p)$ is block-diagonal. In this case, $C_{\sigma' \sigma} (\Lambda, p)$ would be a reducible representation, and the $\ket{p,\sigma}$ with $\sigma$ in any given block, will transform within the same block, i.e., according to an irreducible representation. 

Therefore, it's natural to identity the states of a \emph{specific particle} as those transforming under irreducible representations of the Poincaré group. This approach ensures that a Poincaré transformation can't change the type of particle. To construct such irreducible representation, we'll make use of the Casimir operators of the group. Roughly speaking, the eigenvalues of the Casimir operators labels different irreducible representations, which correspond to Poincaré transformations acting on \emph{different types} of particles. Since those operators commute with all the generators of the group (and so with each group element via the exponential map), their eigenvalues remain constant under any Poincaré transformation, preserving the identification of the particle type. Moreover, states that are transformed into one another within an irreducible state space are interpreted as different states of the same particle.

It's important to emphasise, however, that the eigenvalues of the Casimir operators do \emph{not} uniquely characterise an irreducible representation. For example, as we will see, the Casimirs vanish for all massless (helicity) representations. Since a comprehensive mathematical treatment would be quite technical and wouldn't provide additional physical insight, we'll stick to the interpretation of an irreducible representation as one that can't change the labels which characterise the type of particle. 

Additionally, let's note that physicists often employ an abuse of language by referring to irreducible representations as the states. Keep in mind, however, that the representation is actually the operator acting on the state.

Let's go back to~\eqref{eq:temp-1} and to the problem of working out the structure of the coefficients $C_{\sigma'\sigma}(\Lambda,p)$ in irreducible representations of the Poincaré group. In order to do that, note that the only functions of $p^\mu$ that are left invariant by all transformations $\tensor{\Lambda}{^\mu_\nu} \in SO(1,3)^+$ are $p^2 = \eta_{\mu\nu} p^\mu p^\nu$ and, for $p^2 \leq 0$, also the sign of $p^0$. Hence, for each value of $p^2$, and (for $p^2 \leq 0$) each sign of $p^0$, one can choose a standard four-momentum, say $q^\mu$, and express any $p^\mu$ of this class as
\begin{equation}
    p^\mu = \tensor{L}{^\mu_\nu}(p)q^\nu,
\end{equation}
where $\tensor{L}{^\mu_\nu}$ is some standard proper orthochronous Lorentz transformation that depends on $p^\mu$, and also implicitly on our choice of $q^\mu$. One can then define the states $\ket{p,\sigma}$ of momentum $p^\mu$ by
\begin{equation}\label{eq:temp-2}
    \ket{p,\sigma} \coloneq N(p) U(L(p)) \ket{q,\sigma},
\end{equation}
where $N(p)$ is a numerical normalisation factor. Now, acting on~\eqref{eq:temp-2} with a generic Lorentz transformation $U(\Lambda)$, we find
\begin{equation}\label{eq:temp-3}
    U(\Lambda) \ket{p,\sigma} = N(p) U(L(\Lambda p)) U(L^{-1}(\Lambda p) \Lambda L(p)) \ket{q,\sigma}
\end{equation}
\begin{proof}
    \begin{equation*}
    \begin{split}
        U(\Lambda) \ket{p,\sigma} &= N(p) U(\Lambda) U(L(p)) \ket{q,\sigma} = N(p) U(\Lambda L(p)) \ket{q,\sigma}\\
         &= N(p) U(L(\Lambda p)) U(L^{-1}(\Lambda p) \Lambda L(p)) \ket{q,\sigma} ,
    \end{split}
    \end{equation*}
    where we used the (representation) group composition rule~\eqref{eq:representation-poincare-group-multiplication} two times, together with $L L^{-1} = \1$.
\end{proof}

 The point of this last step is that the Lorentz transformation $L^{-1}(\Lambda p) \Lambda L(p)$ takes $k$ to the following values
\begin{equation}
    k \to p \to \Lambda p \to k .
\end{equation}
Therefore, $L^{-1}(\Lambda p) \Lambda L(p)$ belongs to the \emph{little  group} or \emph{stabiliser group}, i.e., the subgroup made of transformations which leave $q^\mu$ invariant,
\begin{equation}\label{eq:little-group}
    \tensor{W}{^\mu_\nu} q^\nu = q^\mu .
\end{equation}

Using eq.~\eqref{eq:temp-1}, for each $W$ in the little group satisfying~\eqref{eq:little-group}, we have
\begin{equation}
    U(W) \ket{k,\sigma} = \sum_{\sigma'} D_{\sigma'\sigma}(W) \ket{k,\sigma'} ,
\end{equation}
where the coefficients $D(W)$ furnish a representation of the little group. Then, for any $W,\bar{W}$ in the little group,
\begin{equation*}
\begin{split}
    \sum_{\sigma'} D_{\sigma'\sigma} (\bar{W}W) \ket{k,\sigma'} &= U(\bar{W}W)  \ket{k,\sigma} = U(\bar{W}) U(W) \ket{k,\sigma} = U(\bar{W}) \sum_{\sigma''} D_{\sigma''\sigma}(W) \ket{k,\sigma''} \\ &= \sum_{\sigma' \sigma''} D_{\sigma''\sigma}(W) D_{\sigma'\sigma''}(\bar{W}) \ket{k,\sigma'} ,
\end{split}
\end{equation*}
and so
\begin{equation}
    D_{\sigma'\sigma}(\bar{W}W) = \sum_{\sigma''} D_{\sigma'\sigma''} (\bar{W}) D_{\sigma'' \sigma}(W) .
\end{equation}

In particular, for $W(\Lambda,p) \equiv L^{-1}(\Lambda p) \Lambda L(p)$, eq.~\eqref{eq:temp-3} becomes
\begin{equation}
   U(\Lambda) \ket{p,\sigma} = N(p) \sum_{\sigma'} D_{\sigma'\sigma}(W(\Lambda,p))U(L(\Lambda p)) \ket{q,\sigma'} ,
\end{equation}
or, recalling the definition~\eqref{eq:temp-2},
\begin{equation}\label{eq:induced-representation}
    U(\Lambda) \ket{p,\sigma} = \frac{N(p)}{N(\Lambda p)} \sum_{\sigma'} D_{\sigma'\sigma} (W(\Lambda, p)) \ket{\Lambda p, \sigma'} .
\end{equation}

We won't go into the details of the normalisation here. We simply note that, by the usual orthonormalization procedure in quantum mechanics, we may choose states with standard momentum $q^\mu$ to be orthonormal, in the sense that
\begin{equation}
    \braket{k',\sigma'}{k,\sigma} = \delta^{(3)}(\vec{k}' - \vec{k}) \delta_{\sigma'\sigma} ,
\end{equation}
and by suitable choices of the coefficients in~\eqref{eq:induced-representation}, we can normalise states of arbitrary momentum as
\begin{equation}
    \braket{p',\sigma'}{p,\sigma} = \delta^{(3)}(\vec{p}' - \vec{p}) \delta_{\sigma'\sigma} .
\end{equation}

By eq.~\eqref{eq:induced-representation}, the problem of determining the coefficients $C_{\sigma'\sigma}$ in the transformation rule\color{red}\dots\color{black} has been reduced to the problem of determining the coefficients $D_{\sigma'\sigma}$. In other words, the problem of determining all possible irreducible representations of the Poincaré group has been reduced to the problem of finding all possible irreducible representations of the little group, depending on the class of momentum to which $q^\mu$ belongs. This approach of deriving the representations of a group from the representations of its little group is called \emph{method of induced representations}.

